\documentclass{jonthibeault_resume}

\setname{Jon}{Thibeault}
\setaddress{Austin, TX}
\setmobile{832-326-6440}
\setmail{jonthibeault@gmail.com}
\setposition{Software Engineer} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/jon-thibeault/}
\setgithubaccount{https://ihopethisnamefi.github.io/}
\setthemecolor{blue}

\begin{document}
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{
\textbf{Full Stack Software Developer} with over 10 years of experience developing on production facing platforms. Obsessed with high-quality, clean code and documentation. Eager to learn
new technologies and techniques in the field. Passionate about thinking analytically and solving
challenging problems. Enjoys providing exciting features to a wide user base to make their application
experience better and more enjoyable.
}
%
%Education
\section{Education} 
    \datedexperience{University of Notre Dame}{September 2005 - December 2010} 
    \explanation{B.S in Electrical Engineering} 
     \explanationdetail{\coloredbullet\ 
     Senior Project - Wrote the microcontroller code for a robotic football team.
     }
    \datedexperience{Austin Coding Academy}{October 2017 - December 2017} 
    \explanation{Javascript Full Stack Web Dev Course - 100\% Grade} 
    \explanationdetail{\coloredbullet\
     Graduation Project - Created a fantasy football stats web scraper.
     }
%
% Experience
\section{Experience}
    %
    \datedexperience{Hewlett Packard}{July 2010 - November 2015} 
    \explanation{Application Developer}
    \explanationdetail{\coloredbullet\
     Developer for three IT Supply Chain Applications.
     }
    \explanationdetail{\coloredbullet\
     CIO Excellence Customer award for role that won a \$40 million deal for UK and Ireland mid-level suppliers.
     }
    %
    \datedexperience{Hewlett Packard Enterprise}{November 2015 - April 2017} 
    \explanation{Application Developer}
    \explanationdetail{\coloredbullet\
     Lead Developer for Supplier Portal platform.
     }
    \explanationdetail{\coloredbullet\
     Lead Developer for project setting up ETL layer between supply chain systems.
     }
    %
    \datedexperience{DXC Technology}{April 2017 - January 2018} 
    \explanation{Application Developer} 
    \explanationdetail{\coloredbullet\
     Lead Developer for Supplier Portal company spin-off projects.
     }
    %
    \datedexperience{Walmart Technology}{January 2018 - Present} 
    \explanation{Senior Software Engineer} 
    \explanationdetail{\coloredbullet\
     Developer since inception for home-grown, mobile focused platform used globally in all Walmart stores.
     }
    \explanationdetail{\coloredbullet\
     Mentor to junior developers and new team members.
     }
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Typescript \cpshalf Javascript \ \ \textbf{\emph{Familiar:}} \ \  Java \cpshalf Perl \cpshalf Python \cpshalf C \cpshalf C++}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{GIT \cpshalf CLI \cpshalf Agile Methodology \cpshalf DevOps Lifecycle \cpshalf Docker \cpshalf Kubernetes}}
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Angular \cpshalf React \cpshalf React Native \cpshalf Ionic/Cordova \cpshalf Redux \cpshalf Node \cpshalf GraphQL \cpshalf Apollo}}
    %
    \newcommand{\skillfour}{\createskill{Server Technologies}{Azure \cpshalf Heroku \cpshalf OneOps \cpshalf Apache \cpshalf Tomcat \cpshalf Weblogic}}
    %
    \newcommand{\skillfive}{\createskill{Testing Frameworks}{Jasmine \cpshalf Karma \cpshalf Jest \cpshalf Mocha \cpshalf Protractor \cpshalf Selenium Webdriver \cpshalf JUnit}}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive}
%
% Experience
\section{Extra}
    \newcommand{\extraone}{
    Brazilian Jiu Jitsu Black Belt who teaches classes and competes nationwide regularly.
    }
    %
    \newcommand{\extratwo}{
    Enjoys creating fantasy football data import tools, UIs, and bots.
    }
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
    %
    \createbullets{\listofextras}
%
%Footnote
\createfootnote
\end{document}
